---
title: "Testing Programs"
author: "Henrik-Alexander Schubert"
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Motivation
Programs can produce errors. There are several kinds of errors that could arise in programming.


```{r 1try}
# Example function
average <- function(x) {
  sum(x) / length(x)
}
```

## 1. TypeError
Some functions require a specific data type. If you insert the wrong data type, the program breaks.

```{r typeerror}
average(c("1", "2", "3"))
```


### Solution to TypeError: Exceptions
You could use exceptions to return a different outcome instead of breaking the program.

```{r exception}
# Exception method with message
average <- function(x) {
  if (!is.numeric(x)) {
    message("'x' must be a numeric vector. Returning NA instead")
    return(NA)
  }
  sum(x) / length(x)
}
# Exception method with warning
average <- function(x) {
  if (!is.numeric(x)) {
    warning("'x' must be a numeric vector. Returning NA instead")
    return(NA)
  }
  sum(x) / length(x)
}

# Apply the function
average(c("1", "2", "3"))
```

### Contains NA values
Some vectors contain NA values, which may impact the results.

```{r}
average <- function(x) {
  if (!is.numeric(x)) {
    warning("'x' must be a numeric vector. Returning NA instead")
    return(NA)
  }
  if (any(is.na(x))){
    warning("'x' contains one or more NA values.")
    return(NA)
  }
  sum(x) / length(x)
}
```

# Unit tests
Unit tests is some code to test some functions inside of the program.

```{r testfunction}
test_average <- function(){
  if (average(c(1, 2, 3)) == 2) {
    cat("'average' passed the test :) \n")
  } else {
    cat("'average' failed test :( \n")
  }
}

test_average()

```


