---
title: "Packaging"
author: "Henrik-Alexander Schubert"
date: "`r Sys.Date()`"
output: pdf_document
root.dir: "C:/Users/Lenovo/Desktop/Teaching/R_for_social_science/packages/ducksay"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Create the package
if (!file.exists("ducksay")){
  dir.create("packages/ducksay")
}


# Set working directory
#setwd("ducksay")
```

# Structure of a package


- DESCRIPTION: Describes the name, title, license, author and purpose of the package.
- NAMESPACE: Makes the functions available to the user.
- man/:
- R/: the R-code
- tests/:
- ...: additional files


# Create the DESCRIPTION file
A description file should contian the name of the package, a tiltle, a description of the purpose of the package, a Version, an author and the license. Additional information can be provided as well.

- package: 
- Title:
- Description:
- Version: 1.0
- Authors@R:
- License:

```{r}
# Create the description file without extension
file.create("ducksay/DESCRIPTION")

package <- "Package: ducksay"
title <-  "Title: Duck Say2"
description <-   "Description: Say 'hello' with the duck."
version <- "Version: 1.0"
authors <- "Authors@R: person('Henrik-Alexander', 'Schubert', email = 'schubert@demogr.mpg.de', role = c('aut', 'cre'))"

license <- "License: MIT + LICENCE"

# Combine the results
print(rbind(package, title, description, version, authors, license)[, 1])

```

# Creating tests
If you want to include some tests and unit tests, you use the packages 'devtools'. 

# Writing the R code
The folder of the package contains a subdirectory called 'R'. In this folder, there is a R-script with the package-name that contains the functions. 

# Writing the description
The description is written inside the subdirectory 'man', which stands for manual. The folder contains a .Rd-file with the package-name. Inside the file, the description is written in R documentation language.

# Building the package



## Example
In this example, we develop a package that takes a string input and prints a duck, which says the string. The package is going to be called ducksay.


